The Multi-Stencil Language

### 2016-05-30 ARTICLES/IJPP/article/evaluation.tex
Minor re-wording

This section presents evaluations of the work presented in this paper. First, the compiler is evaluated. Second, the data prallelization technique is evaluated, as well as the fusion optimization, and compared to a full SkelGIS program. Third, the hybrid parallelization (data and task) is evaluated and validates the performance model detailed in Section~\ref{sect:tsp}.

@@

The series-parallel tree decomposition $TSP$ of this simulation, extracted by the MSL compiler, is composed of 17~sequence nodes and 18~parallel nodes. Table~\ref{fig:freq} represents the number of time a given level of parallelism, \ie the number of tasks to perform concurrently, is observed in the final tree. One can notice that the level of task parallelism extracted from the Shallow water equations is limited by two sequential parts in the application (level 1). Moreover, a level of 16~parallel tasks is reached two times, and five times for the fourth level.

>>>>

This section presents evaluations of the work presented in this paper. First, the compiler is evaluated. Second, the data parallelization and fusion optimization are evaluated and compared to a full SkelGIS program. Third, the hybrid parallelization (data and task) is evaluated to validate the performance model detailed in Section~\ref{sect:tsp}.

@@

The series-parallel tree decomposition $TSP$ of this simulation, extracted by the MSL compiler, is composed of 17~sequence nodes and 18~parallel nodes. Table~\ref{fig:freq} represents the number of time a given level of parallelism, \ie the number of tasks to perform concurrently, is observed in the final tree. One can notice that the level of task parallelism extracted from the Shallow water equations is limited by two sequential parts in the application (level 1). Moreover, a level of 16~parallel tasks is reached two times, and five times for the fourth level.
This means that if two threads are dedicated to task parallelism, two parts of the code at least will not take advantage of this and that no part of the code would benefit from more than 16 threads.
